Distance Sampling in \proglang{R}

### 2015-12-05 paper.Rmd
remove g(x) plots for amakihi

** ER suggests the g(x) plots for the amakihi be deleted **

```{r minke-amakihi-hn-plot, echo=FALSE, warning=FALSE, fig.width=9, fig.height=6, fig.cap="Top row plots of fitted detection functions overlayed on the histograms of observed distances; left minke whale data, half-normal model; centre, amakihi data hazard-rate with observer as a covariate; right, amakihi data, hazard-rate model with observer and minutes after sunrise as covariates (for amakihi histograms are rescale to take into account sampler geometry). Bottom row shows plots of the probability density function for the amakihi models (as top row). For covariate models (centre and right columns) points indicate probability of detection for a given observation (given that observations covariate values) and lines indicate the average detection function.\\label{fig:minkeamakihi}"}
par(mfrow=c(2,3))
plot(minke_hn, showpoints=FALSE)
plot(amakihi_hr_obs)
plot(amakihi_hr_obs_mas)
plot(1,1, type="n", axes=FALSE, xlab="", ylab="")
plot(amakihi_hr_obs, pdf=TRUE)
plot(amakihi_hr_obs_mas, pdf=TRUE)
```

>>>>

```{r minke-amakihi-hn-plot, echo=FALSE, warning=FALSE, fig.width=9, fig.height=4, fig.cap="Left: fitted detection functions overlayed on the histogram of observed distances for the minke whale data using half-normal model. Centre, right: plots of the probability density function for the amakihi models. Centre, hazard-rate with observer as a covariate; right, hazard-rate model with observer and minutes after sunrise as covariates. Points indicate probability of detection for a given observation (given that observations covariate values) and lines indicate the average detection function.\\label{fig:minkeamakihi}"}
par(mfrow=c(1, 3))
plot(minke_hn, showpoints=FALSE)
plot(amakihi_hr_obs, pdf=TRUE, cex=0.7)
plot(amakihi_hr_obs_mas, pdf=TRUE, cex=0.7)
```
